The Decline of Financial Wellness

### 2023-03-09 outputs/paper/paper3.qmd
changed subtitles

| Variable | New Name               | Description                                                                             | Example               |
|---------|-----------------|----------------------------|------------------|
| satfin   | financial_satisfaction | Respondent's satisfaction with their current financial situation                        | Pretty Well Satisfied |
| finalter | financial_change       | Changes in respondent's financial situation                                             | Stayed the same       |
| finrela  | financial_compare      | Comparing respondent's family income with American families in general                  | Above Average         |
| class    | social_class           | self identified social class the respondent belong in                                   | Middle Class          |
| class1   | social_class1          | self identified social class the respondent belong in (more granular than social_class) | Upper Middle Class    |

@@

### Gaps

@@

### Translations

@@

### Affordances: New Experiments

>>>>

| Variable | New Name               | Description                                                                             | Example               |
|----------------|----------------|-------------------------|----------------|
| satfin   | financial_satisfaction | Respondent's satisfaction with their current financial situation                        | Pretty Well Satisfied |
| finalter | financial_change       | Changes in respondent's financial situation                                             | Stayed the same       |
| finrela  | financial_compare      | Comparing respondent's family income with American families in general                  | Above Average         |
| class    | social_class           | self identified social class the respondent belong in                                   | Middle Class          |
| class1   | social_class1          | self identified social class the respondent belong in (more granular than social_class) | Upper Middle Class    |

@@

### Gap in 2020 data

@@

### "Don't know" responses

@@

### Afordances: New Experiments
